Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-24 mr-review.Rmd
more writing!

@burgess_robust_2020 introduced the contamination mixture method for robust and efficient MR
analysis with hundreds of SNPs, some of which may be invalid instruments by violating one or more of the three core assumptions.

@zhao_statistical_2020 presented MR-RAPS, a method that leverages a robust adjusted profile score to accomplish statistical inference in two-sample MR analyses with GWAS data.

@@

@@

@yuan_likelihood_2021 found that MRMix is not robust to misspecification of SNP effect sizes and often is 
biased. CAUSE, they found, yields overly conservative p-values [@yuan_likelihood_2021].
These observations motivated @yuan_likelihood_2021 to develop a new method, MRAID. MRAID accommodates both individual-level data and GWAS summary statistics [@yuan_likelihood_2021]. We focus on 
the approach that uses GWAS summary statistics. Two equations are central to MRAID modeling (Equations \@ref(mraid1) and \@ref(mraid2)).

@@

@@

>>>>

@burgess_robust_2020 introduced the contamination mixture method for robust and efficient MR
analysis with hundreds of SNPs, some of which may be invalid instruments by violating one or more of the three core MR assumptions.

@zhao_statistical_2020 presented MR-RAPS, a method that leverages a robust adjusted 
profile score to accomplish statistical inference in two-sample MR analyses with GWAS 
summary data. Dividing pleiotropic effects into systematic and idiosyncratic, they model the 
systematic pleiotropy with random effects. In so doing, no SNP satisfies the exclusion 
restriction assumption. Adjusting their profile likelihood estimator from the setting 
without pleiotropy, @zhao_statistical_2020 obtain an estimator with consistency and 
asymptotic normality [@mccullagh_simple_1990]. Idiosyncratic pleiotropy is addressed through robustification of 
the adjusted profile score [@huber_robust_1964]. They then demonstrate the properties of their estimator by 
analyzing simulated and real data [@zhao_statistical_2020].

@@

@hemani_orienting_2017

@windmeijer_use_2019

@@

@yuan_likelihood_2021 found that MRMix is not robust to misspecification of SNP effect sizes and often is 
biased. CAUSE, they found, yields overly conservative p-values [@yuan_likelihood_2021].
These observations motivated @yuan_likelihood_2021 to develop a new method, MRAID. MRAID accommodates both individual-level data and GWAS summary statistics [@yuan_likelihood_2021]. We focus on 
the approach that uses GWAS summary statistics. Two equations are central to MRAID modeling (Equations \@ref(eq:mraid1) and \@ref(eq:mraid2)).

@@

@brown_welch-weighted_2021

@@

## Multivariate exposures in MR analysis

@grant_pleiotropy_2021: we introduce three methods which build on common approaches in the univariable setting: {MVMR}-Robust; {MVMR}-Median; and {MVMR}-Lasso
